Two-Dimensional Vesicle Hydrodynamics from Hydrophobic Attraction Potential

### 2022-02-13 doc/reviews/ResponseToReviewer1.tex

\noindent
\comment{Line 70: ``we maintain contact-free suspensions with a
relatively weak non-stiff repulsive force". What do you mean by
relatively weak repulsive force ? Weak compared to what? (see additional
question on this hereinafter).}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{Equation (2.4) is not necessary as the no-slip boundary
condition is standard and it is redundant with (2.5).}
\begin{itemize}
  \item We deleted the redundant equation (2.5) mentioned by the Reviewer.
\end{itemize}

\noindent
\comment{Section 2.2: for clarity, define the variable u as the
hydrophobic attraction potential in the first paragraph.}

\noindent
\comment{The equations of the continuous time evolution of the particle
positions and orientations should be written in Section 2 to close the
problem.}
\begin{itemize}
  \item Section 2.2 introduces the imposed forces and torques in hydrophobic attraction and repulstion that are not used to obtain particle directions directly. Following the next comment by 
the Reviewer, we agreed that Section 2.3 should be moved to the end of Section 3 and we complete the change.
\end{itemize}

\noindent
\comment{I think the time-discretization Section 2.3 should go at the
end of Section 3 since this is the one devoted to the numerical
discretization of the governing equations. Also, the sentence ``particle
collisions are avoided even when using a relatively large time step" is
very vague.  What do you mean by ``relatively large time step"? Compared
to what time scale?}
\begin{itemize}
  \item We thank the Review for the comment and we moved the original Section 2.3 {\it Time Marching} at the end of Section 3 combining the change based on the comment previously addressed about what to solve for in the proposed algorithm. 
As described in Section 2.2, the repulsion force with a constant strength coefficient $M$ is chosen 
to be a large number in order to avoid particle collisions. If $M$ is not large enough, the hydrophobic attraction will dominate the total force and the dynamics may cause particle collisions with the use of a larger time step. Therefore, with an empirical study to the relationship between 
choices of M and $\gamma$, the parameter set in this work allows the time step to be as large as
$O(10^{-1})$ with no error. Comparing the time step used in literatures, for instance, in Bystricky {\sl et al.}, Int. J. Numer. Methods Fluids), $\Delta t\sim O(10^{-2})$.
\end{itemize}

### 2022-02-14 doc/main_jfm.tex
RJR new Figure2_part1_Wrapper.pdf; new permeability section
delete orig equations (2.5)

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{Figure0_Wrapper.pdf}
\end{center}
\caption{Panel (a) illustrates the domain and boundary conditions for
  the mobility problem. The color map in panels (b)--(e) is the solution
  $u$ of \eqref{eq:SL}. Red is for $u = 1$ and blue is for $u = 0$.
  Particles self-assemble into vesicle bilayers (panel (b)) and
  eventually arrange along inner and outer leaflets. In panel (c), $C_M$
  is the midplane curve, \ReviewerOne{and} $A$ is the enclosed area\ReviewerOne{.}
  %, and $L$ is the arc length. 
  Initially stretched vesicles relax to equilibrium with fluid
  flow across the bilayer. The study considers a single vesicle in
  background flows such as shear flow (panel (d)) and hydrodynamic
  vesicle-vesicle interactions (panel (e)).}
\label{fig:figure0}
\end{figure}

@@

\section{Governing Equations\label{sec:governing_eqs}}
\subsection{\label{mobility}Mobility Problem}
The objective of this work is to study the hydrodynamics of JP vesicles
in background flows. We consider an $N_b$-many body collection of JP
suspended in a two-dimensional unbounded domain $\Omega$. The boundary
of each particle is denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1
\cup \Gamma_2 \cup \cdots \cup \Gamma_{N_b}$ (Figure
\ref{fig:figure0}a). Assuming the inertial terms are negligible, the
governing equations are
\begin{alignat}{3}
\label{eq:stokes}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
    && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
%
where $\uu$ is the velocity, $p$ is the
pressure, $\uu_\infty$ is the background flow, and $\mu$ is the constant viscosity. 
%
Since each particle $\Gamma_i$ with centre $\aa_i$ is a rigid body, its velocity satisfies 
\ReviewerOne{the no-slip boundary condition}
\begin{align}
  \ReviewerOne{\uu}(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
    \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is its translational velocity and $\omega_i$ is its
angular velocity. Here, $\langle x, y \rangle^{\perp} = \langle -y, x
\rangle$.
%Therefore, the no-slip boundary condition on each particle is
%
%
%\begin{align}
%\label{eq:rigid_bc}
%  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
%    \xx \in \Gamma_i.
%\end{align}
%
%
To determine the translational and angular velocities of each particle,
we define imposed forces $\FF_i$ and torques $T_i$ acting on each
particle. Since the small particles are inertialess, force and torque
balance gives 
\begin{alignat}{2}
  \label{eq:force}
  \FF_i &- \int_{\Gamma_i} \ssigma \cdot \nnu \, \dif s = \mathbf{0},
  && i=1,\ldots,N_b,\\
  \label{eq:torque}
  T_i &- \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
    (\ssigma \cdot \nnu) \, \dif s = 0, \qquad && i=1,\ldots,N_b,
\end{alignat}
where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor (pressure tensor) and
$\nnu$ is the particle outward normal. The process of finding the
translational and angular velocities given the forces and torques is
referred to as the mobility problem.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Imposed Forces}
The imposed forces and torques contain two parts: hydrophobic attraction
and repulsion. The hydrophobic attraction potential was introduced
by~\cite{Fu20} and is responsible for forming particle aggregates that
sequester their hydrophobic surface regions (Figure \ref{fig:figure0}b).
We model hydrophobic attraction by solving the screened Laplace equation
boundary value problem
\begin{alignat}{2}
  \label{eq:SL}
-\rho^2 \Delta u + u &=0,            && \xx \in \Omega,\\
\label{eq:SLbc}
u(\xx) &= f_i(\xx),\qquad  && \xx \in \Gamma_i,\; i=1,\ldots,N_b, \\
\label{eq:SLff}
u &\to 0,                          &&|\xx| \to \infty,
\end{alignat}
where $0 \leq f_i \leq 1$ is a material label with $f_i = 0$,
respectively $1$, representing hydrophilic, respectively hydrophobic,
portions of the surface. We assume that both $f_i$ and $\Gamma_i$ are
smooth. The parameter $\rho > 0$ is the decay length of attraction. The
forces and torques of attraction are 
\begin{align}
  \label{eq:hydrophobicAttraction}
  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu \, \dif s, 
    \quad 
  T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot ({\bf T} \cdot \nnu) \dif s,
\end{align}
where
\begin{align}
  \label{eq:stress}
\mathbf{T}
= \gamma\rho^{-1}u^2 \mathbf{I} + 2\rho\gamma \left(\tfrac{1}{2}|\nabla
  u|^2 \mathbf{I} - \nabla u  \nabla u^T\right)
\end{align}
is the hydrophobic stress tensor and $\gamma > 0$ is
the interfacial
tension.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{HAP Boundary Integral Equation}
Similar to our previous work (\cite{Fu20}), we represent the
\ReviewerTwo{hydrophobic attraction potential (HAP)} as a double-layer
potential
\begin{align}
  \label{eq:HAP_DLP}
  u(\xx) = \frac{1}{2\pi} \int_{\bd\Omega} \left(\pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) 
    \sigma(\yy) \, \dif s_\yy, \quad \xx \in \Omega,
\end{align}
where $K_0$ is the zeroth-order modified Bessel function of the first
kind and the integral is taken in the sense of principle value whenever
$\xx \in \partial \Omega$.  By requiring that the density function
$\sigma$ satisfies the second-kind integral equation
\begin{equation}
\label{eq:screenedSKIE}
  f(\xx) = \frac{1}{2}\sigma(\xx) + 
    \frac{1}{2\pi}\int_{\bd\Omega} \left(\pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) \sigma(\yy) \, 
    \dif s_\yy, \quad \xx \in \bd\Omega,
\end{equation}
the HAP double-layer potential~\eqref{eq:HAP_DLP} satisfies the screened
Laplace equation~\eqref{eq:SL}--\eqref{eq:SLff}. After
discretizing~\eqref{eq:screenedSKIE}, the result is an $NN_b \times
NN_b$ linear system that is solved with block-diagonal preconditioned
GMRES.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Main Theoretical Result: Calculating the Hydrophobic Force}
\label{subsec:calculating_force}
Once \eqref{eq:screenedSKIE} has been solved for $\sigma$, we need to
evaluate the integrals~\eqref{eq:hydrophobicAttraction} which are the
HAP forces and torques. These integrals involve the
stress~\eqref{eq:stress} which contains a singular integral for the
gradient of the double-layer potential. To avoid singular integrals, we
first define
\begin{align}
  \label{eq:uidef}
  w_i(\xx) = u(\xx) - u_i(\xx),
\end{align}
where
\begin{align}
  u_i(\xx) &= \frac{1}{2\pi} \int_{\Gamma_i} \left(\pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) 
    \sigma(\yy) \, \dif s_\yy, \quad \xx \in \mathbb{R}^2.
\end{align}
That is, $w_i(\xx)$ is the double-layer potential~\eqref{eq:HAP_DLP}
with $\Gamma_i$ excluded from $\bd\Omega$. Having defined $w_i$, we prove
\begin{theorem}
\begin{align}
  \label{eq:recipforcetorque}
  \FF_i^{\mathrm{hydro}} = \int_{\Gamma_i} \JJ_i \,\dif s,\quad
  T_i^{\mathrm{hydro}}    = \int_{\Gamma_i} 
    (\xx - \aa_i)^{\perp} \cdot \JJ_i  \,\dif s,
\end{align}
where
\begin{align}
  \label{eq:jumpstress1}
  \JJ_{i} = 2\gamma\rho^{-1} \sigma w_i \nnu + 
    2\gamma\rho \frac{d\sigma}{ds} \frac{dw_i}{ds} \nnu -
    2\gamma\rho \frac{d\sigma}{ds} \frac{dw_i}{d\nnu} \ttau.
\end{align}
\end{theorem}
The symbols $\ttau$ and $\frac{d}{ds}$ are the unit tangent and arc
length derivative for $\Gamma_i$, respectively (Figure
\ref{fig:figure0}a.) The result is valid for any smooth particle shape
or boundary condition. The advantage of
using~\eqref{eq:recipforcetorque} over
using~\eqref{eq:hydrophobicAttraction} is that the components $\sigma$,
$w_i$, $\frac{d\sigma}{ds}$, and $\frac{dw_i}{ds}$ of $\JJ_i$ are smooth
functions, whereas the components of \eqref{eq:stress} are singular
integrals.

@@

To prove \eqref{eq:recipforcetorque}, let 
\begin{align*}
  {\bf T} &=
    \SS(u_i,u_i) +(\SS(u_i,w_i) +\SS(w_i,u_i)) +\SS(w_i,w_i) \\
  &= {\bf T}_1 + {\bf T}_2 + {\bf T}_3
\end{align*}
where we introduce the bilinear form
\begin{equation}
\label{eq:Tsplit}
\SS(u,v)
=  \gamma\rho^{-1} uv {\bf I} + \gamma\rho \nabla u \cdot \nabla v {\bf I} - 2 \gamma \rho \nabla u \nabla v^T.
\end{equation}
Using the fact that $u$,  $u_i$, and $w_i$ solve the screened Laplace
equation~\eqref{eq:SL}, and that $\mathbf{T}$, $\mathbf{T}_j$, $j = 1,
2, 3$ are symmetric, it is straightforward to verify that 
  \begin{equation}
    \label{eq:decompdivfree}
    \nabla \cdot {\bf T}_j = 0, \quad
    \nabla \cdot ((\xx-\aa_i)^{\perp} \cdot {\bf T}_j) = 0, \quad j = 1, 2, 3.
  \end{equation}

@@

Let $U_i$ be the interior of the particle indexed by $i$. For $\xx_0
\in \Gamma_i$ and an arbitrary function $g(\xx)$, the notation
\begin{align}
  \jump{g}(\xx_0) = \lim_{\substack{\xx \to \xx_0 \\ \xx \in U_i^c}}g(\xx)  - 
                    \lim_{\substack{\xx \to \xx_0 \\ \xx \in U_i}}g(\xx),
\end{align}
denotes the jump of the limits of $g(\xx)$ taken from the outside to
the inside of $\Gamma_i$.
%\begin{align}
%\lim_{\xx \to \xx_0^+}g(\xx),\quad 
%\lim_{\xx \to \xx_0^-}g(\xx), \quad
%  \jump{g}(\xx_0) = \lim_{\xx \to \xx_0^+}g(\xx)  - \lim_{\xx \to \xx_0^-}g(\xx)
%\end{align}
%denotes the limit taken from points in $U_i^c$,  the limit taken from
%points in $U_i$, and the jump, respectively.  
\begin{lemma}
\begin{align}
  \label{eq:prejump}
  \FF_i^{\mathrm{hydro}} = \int_{\Gamma_i} \jump{{\bf T}_2 \cdot \nnu}  \, \dif s,\quad
  T_i^{\mathrm{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot
  \jump{{\bf T}_2 \cdot \nnu} \, \dif s.
\end{align}
\end{lemma}
\begin{proof}
To show~\eqref{eq:prejump}, we expand \eqref{eq:hydrophobicAttraction} as
\begin{align}
  \FF_i = \int_{\Gamma_i} \left({\bf T}_1 \cdot \nnu + 
    {\bf T}_2 \cdot \nnu + {\bf T}_3 \cdot \nnu \right) \,\dif s.
\end{align}
By~\eqref{eq:uidef} and~\eqref{eq:decompdivfree}, we have that $u_i$ is
smooth and $\nabla \cdot {\bf T}_1 = \mathbf{0}$ in $\mathbb{R}^n
\setminus U_i$. Similarly, $w_i = u - u_i$ is smooth and $\nabla \cdot
{\bf T}_3 = \mathbf{0}$ in $U_i$. By the divergence theorem,  
\begin{align}
  \int_{\Gamma_i}  {\bf T}_1 \cdot \nnu \,\dif s
  = -\int_{\mathbb{R}^n \setminus U_i} \nabla \cdot {\bf T}_1 \,\dif \xx = \mathbf{0},\quad
    \int_{\Gamma_i}  {\bf T}_3 \cdot \nnu\,\dif s
  = \int_{U_i} \nabla \cdot {\bf T}_3 \,\dif \xx = \mathbf{0}.
\end{align}
Finally, $u_i$ and $w_i$ are smooth and $\nabla \cdot {\bf T}_2= 0$ in $U_i$. This gives
\begin{align}
  \mathbf{0} = \int_{U_i} \nabla \cdot {\bf T}_2 \, \dif \xx = \int_{\Gamma_i}  
    ({\bf T}_2 \cdot \nnu)^-\,\dif s,
\end{align}
where the superscript denotes the limit taken from in $U_i$.  
Combining the above gives the first equation in \eqref{eq:prejump}.
The derivation for the second equation in \eqref{eq:prejump} is identical. 
\end{proof}

We have the following jump relations for \eqref{eq:uidef}: 
\begin{equation}
\label{eq:DLjump}
\jump{u_i} = \sigma, \quad
\jump{w_i} = 0, \quad
\jump{\nabla u_i} = \frac{\dif \sigma}{\dif s}\ttau,\quad
\jump{\nabla w_i} = \mathbf{0},
\end{equation}
on $\Gamma_i$ (see, e.g. \cite{KlBaGrON13}). Therefore,
\begin{align*}
  \jump{{\bf T}_2 \cdot \nnu}   &= \jump{\SS(u_i,w_i) \cdot \nnu +
    \SS(w_i,u_i) \cdot \nnu} \\
  &= \Big[\!\Big[ \left( 2\gamma\rho^{-1} u_i w_i \mathbf{I} + 2\gamma\rho \nabla u_i \cdot \nabla w_i \mathbf{I} 
- 2\gamma\rho \nabla u_i  \nabla w_i^T - 2\gamma\rho \nabla w_i \nabla
  u_i^T\right) \cdot \nnu \Big]\!\Big] \\
%  &= \jump{\left( 2\gamma\rho^{-1} u_i v_i \mathbf{I} + 2\gamma\rho \nabla u_i \cdot \nabla v_i \mathbf{I} 
%- 2\gamma\rho \nabla u_i  \nabla v_i^T - 2\gamma\rho \nabla v_i \nabla
%  u_i^T\right) \cdot \nnu}\\
&= 2\gamma\rho^{-1} \sigma w_i \nnu + 2\gamma\rho \frac{d\sigma }{ds}\frac{dw_i }{ds} \nnu
- 2\gamma\rho \ \frac{d\sigma }{ds} \frac{dw_i }{d\nnu} \ttau = \JJ_i.
\end{align*}
%\todo[inline]{RR: Can you make sure the last line is correct? There was
%an unbolded $\nu$ which I changed to a bolded $\nnu$.} RJR -> Correct. Thank you.
Combining this with~\eqref{eq:prejump} gives~\eqref{eq:recipforcetorque}
as required.

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{Figure0_Wrapper.pdf}
\end{center}
\caption{Panel (a) illustrates the domain and boundary conditions for
  the mobility problem. The color map in panels (b)--(e) is the solution
  $u$ of \eqref{eq:SL}. Red is for $\ReviewerTwo{\eta} = 1$ and blue is for $\ReviewerTwo{\eta} = 0$.
  Particles self-assemble into vesicle bilayers (panel (b)) and
  eventually arrange along inner and outer leaflets. In panel (c), $C_M$
  is the midplane curve, \ReviewerOne{and} $A$ is the enclosed area\ReviewerOne{.}
  %, and $L$ is the arc length. 
  Initially stretched vesicles relax to equilibrium with fluid
  flow across the bilayer. The study considers a single vesicle in
  background flows such as shear flow (panel (d)) and hydrodynamic
  vesicle-vesicle interactions (panel (e)).}
\label{fig:figure0}
\end{figure}

@@

\section{Governing Equations\label{sec:governing_eqs}}
\subsection{\label{mobility}Mobility Problem}
The objective of this work is to study the hydrodynamics of JP vesicles
in background flows. We consider an $N_b$-many body collection of JP
suspended in a two-dimensional unbounded domain $\Omega$. The boundary
of each particle is denoted by $\Gamma_i$ so that $\bd \Omega = \Gamma_1
\cup \Gamma_2 \cup \cdots \cup \Gamma_{N_b}$ (Figure
\ref{fig:figure0}a). Assuming the inertial terms are negligible, the
governing equations are
\begin{alignat}{3}
\label{eq:stokes}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, 
    && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
%
where $\uu$ is the velocity, $p$ is the
pressure, $\uu_\infty$ is the background flow, and $\mu$ is the constant viscosity. 
%
Since each particle $\Gamma_i$ with centre $\aa_i$ is a rigid body, its velocity satisfies 
\ReviewerOne{the no-slip boundary condition}
\begin{align}
\label{eq:rigid_bc}
  \ReviewerOne{\uu}(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad 
    \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is its translational velocity and $\omega_i$ is its
angular velocity. Here, $\langle x, y \rangle^{\perp} = \langle -y, x
\rangle$.
%Therefore, the no-slip boundary condition on each particle is
%
%
%\begin{align}
%\label{eq:rigid_bc}
%  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, \quad
%    \xx \in \Gamma_i.
%\end{align}
%
%
To determine the translational and angular velocities of each particle,
we define imposed forces $\FF_i$ and torques $T_i$ acting on each
particle. Since the small particles are inertialess, force and torque
balance gives 
\begin{alignat}{2}
  \label{eq:force}
  \FF_i &- \int_{\Gamma_i} \ssigma \cdot \nnu \, \dif s = \mathbf{0},
  && i=1,\ldots,N_b,\\
  \label{eq:torque}
  T_i &- \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
    (\ssigma \cdot \nnu) \, \dif s = 0, \qquad && i=1,\ldots,N_b,
\end{alignat}
where $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor (pressure tensor) and
$\nnu$ is the particle outward normal. The process of finding the
translational and angular velocities given the forces and torques is
referred to as the mobility problem.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Imposed Forces}
The imposed forces and torques contain two parts: hydrophobic attraction
and repulsion. The hydrophobic attraction potential was introduced
by~\cite{Fu20} and is responsible for forming particle aggregates that
sequester their hydrophobic surface regions (Figure \ref{fig:figure0}b).
We model hydrophobic attraction by solving the screened Laplace equation
boundary value problem
\begin{alignat}{2}
  \label{eq:SL}
-\rho^2 \Delta \ReviewerTwo{\eta} + \ReviewerTwo{\eta} &=0,            && \xx \in \Omega,\\
\label{eq:SLbc}
\ReviewerTwo{\eta}(\xx) &= f_i(\xx),\qquad  && \xx \in \Gamma_i,\; i=1,\ldots,N_b, \\
\label{eq:SLff}
\ReviewerTwo{\eta} &\to 0,                          &&|\xx| \to \infty,
\end{alignat}
where $0 \leq f_i \leq 1$ is a material label with $f_i = 0$,
respectively $1$, representing hydrophilic, respectively hydrophobic,
portions of the surface. We assume that both $f_i$ and $\Gamma_i$ are
smooth. The parameter $\rho > 0$ is the decay length of attraction. The
forces and torques of attraction are 
\begin{align}
  \label{eq:hydrophobicAttraction}
  \FF_i^{\text{hydro}} = \int_{\Gamma_i} {\bf T}\cdot \nnu \, \dif s, 
    \quad 
  T_i^{\text{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot ({\bf T} \cdot \nnu) \dif s,
\end{align}
where
\begin{align}
  \label{eq:stress}
\mathbf{T}
= \gamma\rho^{-1}\ReviewerTwo{\eta}^2 \mathbf{I} + 2\rho\gamma \left(\tfrac{1}{2}|\nabla
  \ReviewerTwo{\eta}|^2 \mathbf{I} - \nabla \ReviewerTwo{\eta}  \nabla \ReviewerTwo{\eta}^T\right)
\end{align}
is the hydrophobic stress tensor and $\gamma > 0$ is
the interfacial
tension.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{HAP Boundary Integral Equation}
Similar to our previous work (\cite{Fu20}), we represent the
\ReviewerTwo{hydrophobic attraction potential (HAP)} as a double-layer
potential
\begin{align}
  \label{eq:HAP_DLP}
  \ReviewerTwo{\eta}(\xx) = \frac{1}{2\pi} \int_{\bd\Omega} \left(\pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) 
    \sigma(\yy) \, \dif s_\yy, \quad \xx \in \Omega,
\end{align}
where $K_0$ is the zeroth-order modified Bessel function of the first
kind and the integral is taken in the sense of principle value whenever
$\xx \in \partial \Omega$.  By requiring that the density function
$\sigma$ satisfies the second-kind integral equation
\begin{equation}
\label{eq:screenedSKIE}
  f(\xx) = \frac{1}{2}\sigma(\xx) + 
    \frac{1}{2\pi}\int_{\bd\Omega} \left(\pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) \sigma(\yy) \, 
    \dif s_\yy, \quad \xx \in \bd\Omega,
\end{equation}
the HAP double-layer potential~\eqref{eq:HAP_DLP} satisfies the screened
Laplace equation~\eqref{eq:SL}--\eqref{eq:SLff}. After
discretizing~\eqref{eq:screenedSKIE}, the result is an $NN_b \times
NN_b$ linear system that is solved with block-diagonal preconditioned
GMRES.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Main Theoretical Result: Calculating the Hydrophobic Force}
\label{subsec:calculating_force}
Once \eqref{eq:screenedSKIE} has been solved for $\sigma$, we need to
evaluate the integrals~\eqref{eq:hydrophobicAttraction} which are the
HAP forces and torques. These integrals involve the
stress~\eqref{eq:stress} which contains a singular integral for the
gradient of the double-layer potential. To avoid singular integrals, we
first define
\begin{align}
  \label{eq:uidef}
  w_i(\xx) = \ReviewerTwo{\eta}(\xx) - \ReviewerTwo{\eta}_i(\xx),
\end{align}
where
\begin{align}
  \ReviewerTwo{\eta}_i(\xx) &= \frac{1}{2\pi} \int_{\Gamma_i} \left(\pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right)\right) 
    \sigma(\yy) \, \dif s_\yy, \quad \xx \in \mathbb{R}^2.
\end{align}
That is, $w_i(\xx)$ is the double-layer potential~\eqref{eq:HAP_DLP}
with $\Gamma_i$ excluded from $\bd\Omega$. Having defined $w_i$, we prove
\begin{theorem}
\begin{align}
  \label{eq:recipforcetorque}
  \FF_i^{\mathrm{hydro}} = \int_{\Gamma_i} \JJ_i \,\dif s,\quad
  T_i^{\mathrm{hydro}}    = \int_{\Gamma_i} 
    (\xx - \aa_i)^{\perp} \cdot \JJ_i  \,\dif s,
\end{align}
where
\begin{align}
  \label{eq:jumpstress1}
  \JJ_{i} = 2\gamma\rho^{-1} \sigma w_i \nnu + 
    2\gamma\rho \frac{d\sigma}{ds} \frac{dw_i}{ds} \nnu -
    2\gamma\rho \frac{d\sigma}{ds} \frac{dw_i}{d\nnu} \ttau.
\end{align}
\end{theorem}
The symbols $\ttau$ and $\frac{d}{ds}$ are the unit tangent and arc
length derivative for $\Gamma_i$, respectively (Figure
\ref{fig:figure0}a.) The result is valid for any smooth particle shape
or boundary condition. The advantage of
using~\eqref{eq:recipforcetorque} over
using~\eqref{eq:hydrophobicAttraction} is that the components $\sigma$,
$w_i$, $\frac{d\sigma}{ds}$, and $\frac{dw_i}{ds}$ of $\JJ_i$ are smooth
functions, whereas the components of \eqref{eq:stress} are singular
integrals.

@@

To prove \eqref{eq:recipforcetorque}, let 
\begin{align*}
  {\bf T} &=
    \SS(\ReviewerTwo{\eta}_i,\ReviewerTwo{\eta}_i) +(\SS(\ReviewerTwo{\eta}_i,w_i) +\SS(w_i,\ReviewerTwo{\eta}_i)) +\SS(w_i,w_i) \\
  &= {\bf T}_1 + {\bf T}_2 + {\bf T}_3
\end{align*}
where we introduce the bilinear form
\begin{equation}
\label{eq:Tsplit}
\SS(\ReviewerTwo{\eta},v)
=  \gamma\rho^{-1} \ReviewerTwo{\eta}v {\bf I} + \gamma\rho \nabla \ReviewerTwo{\eta} \cdot \nabla v {\bf I} - 2 \gamma \rho \nabla \ReviewerTwo{\eta} \nabla v^T.
\end{equation}
Using the fact that $\ReviewerTwo{\eta}$,  $\ReviewerTwo{\eta}_i$, and $w_i$ solve the screened Laplace
equation~\eqref{eq:SL}, and that $\mathbf{T}$, $\mathbf{T}_j$, $j = 1,
2, 3$ are symmetric, it is straightforward to verify that 
  \begin{equation}
    \label{eq:decompdivfree}
    \nabla \cdot {\bf T}_j = 0, \quad
    \nabla \cdot ((\xx-\aa_i)^{\perp} \cdot {\bf T}_j) = 0, \quad j = 1, 2, 3.
  \end{equation}

@@

Let $U_i$ be the interior of the particle indexed by $i$. For $\xx_0
\in \Gamma_i$ and an arbitrary function $g(\xx)$, the notation
\begin{align}
  \jump{g}(\xx_0) = \lim_{\substack{\xx \to \xx_0 \\ \xx \in U_i^c}}g(\xx)  - 
                    \lim_{\substack{\xx \to \xx_0 \\ \xx \in U_i}}g(\xx),
\end{align}
denotes the jump of the limits of $g(\xx)$ taken from the outside to
the inside of $\Gamma_i$.
%\begin{align}
%\lim_{\xx \to \xx_0^+}g(\xx),\quad 
%\lim_{\xx \to \xx_0^-}g(\xx), \quad
%  \jump{g}(\xx_0) = \lim_{\xx \to \xx_0^+}g(\xx)  - \lim_{\xx \to \xx_0^-}g(\xx)
%\end{align}
%denotes the limit taken from points in $U_i^c$,  the limit taken from
%points in $U_i$, and the jump, respectively.  
\begin{lemma}
\begin{align}
  \label{eq:prejump}
  \FF_i^{\mathrm{hydro}} = \int_{\Gamma_i} \jump{{\bf T}_2 \cdot \nnu}  \, \dif s,\quad
  T_i^{\mathrm{hydro}} = \int_{\Gamma_i} (\xx - \aa_i)^{\perp} \cdot
  \jump{{\bf T}_2 \cdot \nnu} \, \dif s.
\end{align}
\end{lemma}
\begin{proof}
To show~\eqref{eq:prejump}, we expand \eqref{eq:hydrophobicAttraction} as
\begin{align}
  \FF_i = \int_{\Gamma_i} \left({\bf T}_1 \cdot \nnu + 
    {\bf T}_2 \cdot \nnu + {\bf T}_3 \cdot \nnu \right) \,\dif s.
\end{align}
By~\eqref{eq:uidef} and~\eqref{eq:decompdivfree}, we have that $u_i$ is
smooth and $\nabla \cdot {\bf T}_1 = \mathbf{0}$ in $\mathbb{R}^n
\setminus U_i$. Similarly, $w_i = \ReviewerTwo{\eta} - \ReviewerTwo{\eta}_i$ is smooth and $\nabla \cdot
{\bf T}_3 = \mathbf{0}$ in $U_i$. By the divergence theorem,  
\begin{align}
  \int_{\Gamma_i}  {\bf T}_1 \cdot \nnu \,\dif s
  = -\int_{\mathbb{R}^n \setminus U_i} \nabla \cdot {\bf T}_1 \,\dif \xx = \mathbf{0},\quad
    \int_{\Gamma_i}  {\bf T}_3 \cdot \nnu\,\dif s
  = \int_{U_i} \nabla \cdot {\bf T}_3 \,\dif \xx = \mathbf{0}.
\end{align}
Finally, $u_i$ and $w_i$ are smooth and $\nabla \cdot {\bf T}_2= 0$ in $U_i$. This gives
\begin{align}
  \mathbf{0} = \int_{U_i} \nabla \cdot {\bf T}_2 \, \dif \xx = \int_{\Gamma_i}  
    ({\bf T}_2 \cdot \nnu)^-\,\dif s,
\end{align}
where the superscript denotes the limit taken from in $U_i$.  
Combining the above gives the first equation in \eqref{eq:prejump}.
The derivation for the second equation in \eqref{eq:prejump} is identical. 
\end{proof}
